---
title: "Forecasting Elantra Sales - MIT edX"
author: "Felipe Nakanishi"
date: "27/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

An important application of linear regression is understanding sales. Consider 
a company that produces and sells a product. In a given period, if the company 
produces more units than how many consumers will buy, the company will not earn 
money on the unsold units and will incur additional costs due to having to store 
those units in inventory before they can be sold. If it produces fewer units 
than how many consumers will buy, the company will earn less than it potentially 
could have earned. Being able to predict consumer sales, therefore, is of first 
order importance to the company.

In this problem, we will try to predict monthly sales of the Hyundai Elantra in 
the United States. The Hyundai Motor Company is a major automobile manufacturer 
based in South Korea. The Elantra is a car model that has been produced by Hyundai 
since 1990 and is sold all over the world, including the United States. We will 
build a linear regression model to predict monthly sales using economic indicators 
of the United States as well as Google search queries.

The file elantra.csv contains data for the problem. Each observation is a month, 
from January 2010 to February 2014. For each month, we have the following variables:

* Month = the month of the year for the observation (1 = January, 2 = February, 3 = March, ...).
* Year = the year of the observation.
* ElantraSales = the number of units of the Hyundai Elantra sold in the United States 
in the given month.
* Unemployment = the estimated unemployment percentage in the United States in the 
given month.
* Queries = a (normalized) approximation of the number of Google searches for 
"hyundai elantra" in the given month.
* CPI_energy = the monthly consumer price index (CPI) for energy for the given month.
* CPI_all = the consumer price index (CPI) for all products for the given month; 
this is a measure of the magnitude of the prices paid by consumer households for 
goods and services (e.g., food, clothing, electricity, etc.).

## Problem 1 - Loading the Data

Load the data set. Split the data set into training and testing sets as follows: 
place all observations for 2012 and earlier in the training set, and all 
observations for 2013 and 2014 into the testing set.

How many observations are in the training set?
```{r}
data = read.csv('elantra.csv')
train = subset(data, Year <= 2012)
test = subset(data, Year > 2012)
str(train)
```
##  2.1 - A Linear Regression Model

Build a linear regression model to predict monthly Elantra sales using Unemployment,
CPI_all, CPI_energy and Queries as the independent variables. 
Use all of the training set data to do this.

What is the model R-squared? Note: In this problem, we will always be asking 
for the "Multiple R-Squared" of the model.

```{r}
model=lm(ElantraSales~Unemployment + CPI_all + CPI_energy + Queries, data = train)
summary(model)
```
## Problem 2.2 - Significant Variables

How many variables are significant, or have levels that are significant? 
Use 0.10 as your p-value cutoff.

answer: looking at the column 'Pr(>|t|)' of the variables, we can conclude that
none of them are significant at 0.1 of confidence.

## Problem 3.1 - Modeling Seasonality

Our model R-Squared is relatively low, so we would now like to improve our model.
In modeling demand and sales, it is often useful to model seasonality. 
Seasonality refers to the fact that demand is often cyclical/periodic in time. 
For example, in countries with different seasons, demand for warm outerwear 
(like jackets and coats) is higher in fall/autumn and winter (due to the colder 
weather) than in spring and summer. (In contrast, demand for swimsuits and 
sunscreen is higher in the summer than in the other seasons.) Another example is 
the "back to school" period in North America: demand for stationary (pencils, 
notebooks and so on) in late July and all of August is higher than the rest of 
the year due to the start of the school year in September.

In our problem, since our data includes the month of the year in which the units 
were sold, it is feasible for us to incorporate monthly seasonality. From a 
modeling point of view, it may be reasonable that the month plays an effect in 
how many Elantra units are sold.

To incorporate the seasonal effect due to the month, build a new linear regression 
model that predicts monthly Elantra sales using Month as well as Unemployment, 
CPI_all, CPI_energy and Queries. Do not modify the training and testing data frames 
before building the model.

What is the model R-Squared?
```{r}
model_seasonal=lm(ElantraSales ~ Month+Unemployment+CPI_all+CPI_energy+Queries, data=train)
summary(model_seasonal)
```
## Problem 4.1 - A New Model

Re-run the regression with the Month variable modeled as a factor variable. 
(Create a new variable that models the Month as a factor (using the as.factor 
function) instead of overwriting the current Month variable. We'll still use the 
numeric version of Month later in the problem.)

What is the model R-Squared?

```{r}
train$Month1=as.factor(train$Month)
model_new=lm(ElantraSales ~ Month1+Unemployment+CPI_all+CPI_energy+Queries, data=train)
summary(model_new)
```
## Problem 5.1 - Multicolinearity

Another peculiar observation about the regression is that the sign of the 
Queries variable has changed. In particular, when we naively modeled Month as 
a numeric variable, Queries had a positive coefficient. Now, Queries has a 
negative coefficient. Furthermore, CPI_energy has a positive coefficient -- as 
the overall price of energy increases, we expect Elantra sales to increase, 
which seems counter-intuitive (if the price of energy increases, we'd expect 
consumers to have less funds to purchase automobiles, leading to lower Elantra sales).

As we have seen before, changes in coefficient signs and signs that are counter 
to our intuition may be due to a multicolinearity problem. To check, compute the 
correlations of the variables in the training set.

Which of the following variables is CPI_energy highly correlated with? Select 
all that apply. (Include only variables where the absolute value of the correlation
exceeds 0.6. For the purpose of this question, treat Month as a numeric variable, 
not a factor variable.)

answer: Year, unemployment, Queries, CPI_all.

```{r}
cor(train[,-8])
```
## Problem 6.1 - A Reduced Model

Let us now simplify our model (the model using the factor version of the Month 
variable). We will do this by iteratively removing variables, one at a time. 
Remove the variable with the highest p-value (i.e., the least statistically 
significant variable) from the model. Repeat this until there are no variables 
that are insignificant or variables for which all of the factor levels are 
insignificant. Use a threshold of 0.10 to determine whether a variable is 
significant.

Which variables, and in what order, are removed by this process?

```{r}
model_new2=step(model_new)
summary(model_new2)
```
## Problem 6.2 - Test Set Predictions

Using the model from Problem 6.1, make predictions on the test set. 
What is the sum of squared errors of the model on the test set?

```{r}
test$Month1=as.factor(test$Month)
regression = predict(model_new2, newdata=test)
SSE = sum((regression - test$ElantraSales)^2)
SSE
```
## Problem 6.3 - Comparing to a Baseline

What would the baseline method predict for all observations in the test set?
Remember that the baseline method we use predicts the average outcome of all 
observations in the training set.

```{r}

SST = sum((mean(train$ElantraSales)-test$ElantraSales)^2)
SST
```
## Problem 6.4 - Test Set R-Squared

What is the test set R-Squared?
```{r}
R2 = 1 - (SSE/SST)
R2
```
## Problem 6.5 - Absolute Errors

What is the largest absolute error that we make in our test set predictions?
```{r}
max(abs(test$ElantraSales-regression))
```
## Problem 6.6 - Month of Largest Error

In which period (Month,Year pair) do we make the largest absolute error in our prediction?
```{r}
test$dif = abs(test$ElantraSales - regression)
which.max(test$dif)
test[5,]
```
